\documentclass[line,margin]{res}

\let\olditemize\itemize
\renewcommand{\itemize}{
  \olditemize
  \setlength{\itemsep}{-2pt}
}



%padding and margins
\voffset=0in
\oddsidemargin=0pt
\headheight=0pt
\topmargin=0in
\headsep=0in
\textheight=10in


\begin{document}

\name{Lee J. Avital}
\address{leeavital@gmail.com}

\begin{resume}

\section{WORK EXPERIENCE}

{\bf Datadog} \hfill October 2018 - January 2022 \\
\begin{itemize}
  \item \textit{October 2022 - Present, Engineering Manager} managed a group of 14, responsible for both Datadog's cloud-centric and datacenter-centric network monitoring products.
  \item \textit{January 2019 - October 2022, Engineering Team Lead} led a team of between 4 and 10, responsible for Datadog's Network Performance Monitoring product.
  \item \textit{October 2018 - January 2019, Software Engineer} contributed to Datadog's Network Performance Monitoring product, responsible for building and operating a backend for processing tens of thousands of hosts worth of Network traffic.
\end{itemize}

{\bf Palantir Technologies} \hfill June 2015 - October 2018 \\
Software Engineer
\begin{itemize}
\item Contributed to the first version of Palantir Apollo -- a continuous delivery system responsible for automatically, continuously upgrading services then deployed in over 100 isolated customer environments.
\item Contributor to a distributed registry used to provide organization, authorization, and search for datasets and analyses within the Palantir Foundry ecosystem. Implementing the first version of the authorization framework, and search.
\item Contributed to a federated authentication and authorization service used widely across the company.
\end{itemize}

% {\bf  Rochester Institute of Technology} \hfill January 2015 - May 2015 \\
% MLton Undergraduate Infrastructure Support
% \begin{itemize}
% \item Instrumented the LLVM backend of the MLton Standard ML compiler to look for bugs.
% \end{itemize}

{\bf Twitter} \hfill August 2014 - December 2014 \\
Software Engineer Intern
\begin{itemize}
\item Implemented web previews for iOS and Android ads to improve the experience of users setting up mobile ad campaigns.
\item Implemented endpoints and database infrastructure for a new type of ad campaign.
\end{itemize}

{\bf Drawbridge} \hfill May 2014 - August 2014 \\
Platform Intern, KPCB Engineering Fellow
\begin{itemize}
\item Developed a prototype for moving payments processing away from a monolithic batch involving MySQL to a more scalable Kafka approach.
\item Built an internal tool for monitoring application-level metrics.
\end{itemize}

{\bf Massdrop Inc.} \hfill May 2013 - September 2013\\
Engineer Intern, Full Stack

{\bf  National Technical Institute for the Deaf at RIT} \hfill May 2012 - May 2013\\
Web Applications Programmer, Full Stack

\section{PORTFOLIO}

\begin{itemize}
\item {\bf Personal Website}  {\sl http://leeavital.com}
\item {\bf Github} {\sl  https://github.com/leeavital }
\end{itemize}


\section{EDUCATION}   Rochester Institute of Technology \\
                      B.S. in  Computer Science,  Minor in Music and Technology, May 2015 \\

\end{resume}
\end{document}
