\documentclass[line,margin]{res}

\let\olditemize\itemize
\renewcommand{\itemize}{
  \olditemize
  \setlength{\itemsep}{-2pt}
}



%padding and margins
\voffset=0in
\oddsidemargin=0pt
\headheight=0pt
\topmargin=0in
\headsep=0in
\textheight=10in


\begin{document}

\name{Lee J. Avital}
\address{(646) 320-9143\\leeavital@gmail.com}


\begin{resume}

\section{EDUCATION}   Rochester Institute of Technology \\
                      B.S. in  Computer Science,  expected May 2015 \\
<<<<<<< HEAD:bonsai/content/resume/static/resume.tex
	                    Minor in Music and Technology\\
	                    Dean's List: Fall 2011 - Present
=======
                      Minor in Music and Technology\\
                      Dean's List: Fall 2011 - Present
>>>>>>> jekyll:jsite/resume/resume.tex

\section{SPECIAL COURSEWORK}
\begin{itemize}
   \item Compiler Construction (spring 2014)
   \item Programming Language Theory (fall 2013)
   \item Aspect Oriented Programming (fall 2013)
   \item Language and Technology (spring 2013)
\end{itemize}


\section{PORTFOLIO}

\begin{itemize}
   \item {\bf Personal Website}  {\sl http://leeavital.com}
   \item {\bf Github} {\sl  https://github.com/leeavital }
\end{itemize}



\section{PROJECTS}

\begin{itemize}


\item {\bf LeadSheet} A python application that reads a series of chords and
   generates a musical accompaniment in MIDI. Includes a front-end written in
   python/flask.

\item {\bf Volumetric Display} a 3-D display that achieves depth through the
   use of a spinning mirror and a single projection
   (part of a group of 15 people).

\item {\bf SNAP (Shared Namespace Application Programming)}
   A PHP microframework that drastically simplifies AJAX requests by
   exposing selected PHP functions through an automatically generated
   javascript API.


\item {\bf Erlang-Chat}   A multi-client chat server written in Erlang with a
   client written in Java/Swing.



\item {\bf LazyJSON}  A lazy JSON parser written in the D programming language.


\end{itemize}

\section{WORK EXPERIENCE}

{\bf MLton Undergraduate Infrastructure Support} \hfill January 2015 - Present
  Rochester Institute of Technology
  \begin{itemize}
    \item Refactor LLVM codegenerator for the MLton Standard ML compiler
  \end{itemize}

{\bf Engineer Intern} \hfill August 2014 - December 2014 \\
  Twitter Inc.
  \begin{itemize}
  \item Designed and implemented infrastructure for a new type of ad targeting
  \item Implemented the ability to preview tweets and cards for several platforms in the browser
  \end{itemize}

{\bf Platform Intern, KPCB Engineering Fellow} \hfill May 2014 - August 2014 \\
    Drawbridge Inc.

    \begin{itemize}
    \item Migrated infrastructure for processing charges from MySQL-based architecture
    to a Kafka-based architecture
    \item Built out monitoring infrastructure and a visualization tool
    \end{itemize}

{\bf Developer Intern} \hfill May 2013 - September 2013\\
    Massdrop Inc.
    \begin{itemize}
    \item Built new interfaces from the ground up to aid in user education and engagement
    \item Built an internal tool to manage site content and keep track of active shipments
    \item Assisted redesigning/refactoring site architecture
    \end{itemize}

{\bf Web Applications Programmer} \hfill May 2012 - May 2013\\
    National Technical Institute for the Deaf at RIT,
  Rochester, NY

  \begin{itemize} % reduce space between items
  \item Built a file repository applications for instructors and students to manage their course content
  \item Maintained several legacy applications in ASP classic including an online sign language dictionary
  \end{itemize}

\end{resume}
\end{document}
